%access your MikTex Console/distribution --> Packages --> Search for ''resumecls''  --> highlight --> click + to install

\documentclass[11pt,overlapped,line,letterpaper]{res}
\usepackage[T1]{fontenc}
\usepackage[none]{hyphenat}
\usepackage{txfonts}
\usepackage{xcolor}
\newsectionwidth{0pt}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{multicol}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}

\setlength{\headsep}{0.3in}
\rhead{\textsc{\textrm{Gedeon J. Lim}}}
\lfoot{September 2019}

\pagestyle{fancy} % set pagestyle for the document
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\fancyfoot[C]{}

\setlength\parindent{0pt}
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in} \setlength{\itemindent}{-1.6em}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0.5in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in} 
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in}
      \setlength{\leftmargin}{0in}}}{\end{list}}

\begin{document}
\thispagestyle{empty}
\setlength{\parindent}{0cm}{\textsc{\textrm{\textbf{{\Large{Gedeon J. Lim}}}}} \\
270 Bay State Rd, Room 314   \\
Boston University, Department of Economics\\
Boston MA  02215 USA  \\
Cell: (617) 949-1882 \\
Email: \href{mailto:gedeonl@bu.edu}{gedeonl@bu.edu}  \\
Website: \href{https://sites.google.com/a/bu.edu/gedeonlim}{https://sites.google.com/a/bu.edu/gedeonlim} \\
}
\begin{resume}

\section{\textbf{\textsc{Education}}}
\begin{list1}
\item[] Ph.D. Student, Economics, Boston University, Boston MA, 2020 (expected) \\
Dissertation Title: {\it Essays on Development Economics} \\
Main Advisors: Samuel Bazzi \& Dilip Mookherjee \\
Dissertation Committee: Samuel Bazzi, Dilip Mookherjee and Robert A. Margo
\vspace{7pt}
\item[] B.Soc.Sci. Economics, \emph{First Class Honors}, National University of Singapore, Singapore 2014
\end{list1}
\vspace{-4.5pt}

\section{\textbf{\textsc{Fields of Interest}}}
\begin{list1}
\item[] Development Economics, Political Economy, Economic History
\end{list1}
\vspace{-4.5pt}

%\section{\textbf{\textsc{Published Papers}}}
%\begin{list1}
%\item[] 
%\end{list1}
%\vspace{-4.5pt}

\section{\textbf{\textsc{Working Papers}}}
\begin{list1}
\item[] "Why Pay the Chief? Land Rents and Political Selection in Indonesia (Job Market Paper)"
\end{list1}

\vspace{-4.5pt}
\section{\textbf{\textsc{Work in Progress}}}
\begin{list1}
\item[] "The Effects of Long-Run Ethnic Segregation in Southeast Asia"
\end{list1}

\section{\textbf{\textsc{Conferences and Presentations}}}
\begin{list1}
\item[] Northeast Universities Development Conference. Evanston, IL \hfill{2019}
\item[] Economic History Association Meeting, Poster Session. Atlanta, GA \hfill{2019}
\item[] Southeast Asia Research Group N.A. Meeting. Vancouver, Canada \hfill{2019}
\item[] 17th Nordic Conference on Development Economics. Helsinki, Finland \hfill {2018}
\item[] Summer School in Development Economics. Prato, Italy \hfill {2017}
\end{list1}
\vspace{-4.5pt}

\vspace{-4.5pt}
\section{\textbf{\textsc{Grants}}}
\begin{list1}
\item[] Manuel Abdala Gift Grant \hfill{Spring 2019}
\item[] Boston University Initiative on Cities, Seed Funding \hfill{Fall 2018} 
\item[] Graduate Research Abroad Fellowship (Short-Term) \hfill{Fall 2018} 
\item[] Economics Department Summer Research Grant \hfill{Summer 2018} 
\item[] Global Development Policy Center, Summer in the Field \hfill{Summer 2018} 
\end{list1}
\vspace{-4.5pt}

%\item[] Manuel Abdala Gift Grant (Malaysia) \hfill{\$8,000 Spring 2020}
%\item[] Boston University Initiative on Cities, Seed Funding (Malaysia) \hfill {\$9,000 Fall 2018} 
%\item[] Graduate Research Abroad Fellowship (Short-Term) (Indonesia) \hfill{\$4,500 Fall 2018} 
%\item[] Economics Department Summer Research Grant (Indonesia) \hfill{\$5,000 Summer 2018} 
%\item[] GDP Center Summer in the Field (Indonesia) \hfill{\$4,000 Summer 2018} 

%\section{\textbf{\textsc{Conferences and Presentations}}}
%\begin{list1}
%\item[] American Law and Economics Association, Boston, MA 2018
%\item[] Association of Education and Finance Policy, Portland, OR 2017
%\item[] Human Capital and Economic Opportunity Summer School, Chicago, IL 2016
%\end{list1}
%\vspace{-4.5pt}
%
%\section{\textbf{\textsc{Grants}}}
%\begin{list1}
%\item[] ``Crime and Public Housing: A General Equilibrium Analysis," Boston University Initiative on Cities Early Stage Urban Research Award, 2017, \$7,000
%\item[] ``Interdistrict School Choice," Boston University Summer Research Grant, 2017, \$5,000
%\end{list1}
%\vspace{-4.5pt}

\section{\textbf{\textsc{Work Experience}}}
\begin{list1}
\item[] Research Assistant for S. Bazzi, Boston University, \hfill{2015-Present}
\item[] Visiting Researcher, AKATIGA, Indonesia, \hfill{2018}
\item[] Visiting Junior Researcher, SMERU Research Institute, Indonesia \hfill{Summer 2015, 2016}
\item[] Research Assistant for R. Arunachalam \& A. Shenoy, University of Michigan, MI \hfill{Summer 2013}
\item[] Communications \& Research Intern, Centre for Microfinance,  India \hfill{Summer 2012}
\vspace{7pt}
\item[] Non-Commissioned Officer, Singapore Armed Forces, Singapore \hfill{2009-2011}
\end{list1}
\vspace{-4.5pt}

%\section{\textbf{\textsc{Referee Experience}}}
%\begin{list1}
%\item[] Journal of Labor Economics, The RAND Journal of Economics
%\end{list1}
%\vspace{-4.5pt}

%\section{\textbf{\textsc{Teaching Experience}}}
%\begin{list1}
%\item[] Teaching Assistant, Introduction to Health Economics, Department of Economics, Boston University, Spring 2017
%\item[] Teaching Assistant, Environmental Economics, Department of Economics, Boston University, Fall 2016 and Spring 2017
%\item[] Teaching Fellow, Introductory Microeconomic Analysis, Department of Economics, Boston University, 2014-2016
%\item[] Instructor, Economics, Boston University Summer Challenge, Summer 2014
%\item[] Instructor, Precalculus and Advanced Mathematical Decision Making, Springfield Renaissance School, 2012-2013
%\item[] Teaching Assistant, Calculus for the Life and Social Sciences, University of Massachusetts, Amherst, 2010-2011
%\end{list1}
%\vspace{-4.5pt}

%\section{\textbf{\textsc{Departmental Service}}}
%\begin{list1}
%\item[] Organizer, Development Reading Group, 2018-Present
%\item[] Co-Captain, Economics Department Intramural Soccer Team, 2017-Present
%\end{list1}
%\vspace{-4.5pt}

\newpage

\begin{flushleft}
\textbf{\textsc{Languages:}} 
\begin{list1}
\item[] English (native), Mandarin Chinese (native), Bahasa Indonesia (intermediate)
\end{list1}
\end{flushleft}
\vspace{-15pt}

\begin{flushleft}
\textbf{\textsc{Computer Skills:}} ArcGIS, Stata
\end{flushleft}
\vspace{-15pt}

\begin{flushleft}
\textbf{\textsc{Citizenship:}} Singapore/F1
\end{flushleft}
\vspace{-15pt}

\begin{flushleft}
\textbf{\textsc{References}}
\end{flushleft}
\vspace{-15pt}
\begin{multicols}{3}
{\bf Professor Samuel Bazzi} \\
(Co-Chair) \\
Department of Economics \\
Boston University \\
Phone: (617) 353-6150 \\ 
Email: \href{mailto:sbazzi@bu.edu}{sbazzi@bu.edu} \\

{\bf Professor Dilip Mookherjee} \\
(Co-Chair) \\
Department of Economics \\
Boston University \\
Phone: (617) 353-4392 \\ 
Email: \href{mailto:dilipm@bu.edu}{dilipm@bu.edu} \\

{\bf Professor Robert A. Margo} \\
Department of Economics \\
Boston University \\
Phone: (617) 353-6819 \\ 
Email: \href{mailto:margora@bu.edu}{margora@bu.edu} \\
\end{multicols}
\end{resume}

\newpage
\thispagestyle{empty}
\setlength{\parindent}{0cm}{\textsc{\textrm{\textbf{{\Large{Gedeon J. Lim}}}}} \\
\begin{resume}
{\bf Why Pay the Chief? Political Selection \& Economic Development in Indonesia} (Job Market Paper) 
Much of modern development efforts are channeled through traditional local governance. Yet, despite their importance as politician-bureaucrats, traditional chiefs are rarely paid a living wage. This paper studies the effect of awarding chiefs control over rice land -- a stable, revenue generating asset -- during their term of office in rural Indonesia. Using an RD estimator at a colonial border discontinuity, I find a strong positive effect on both historical and contemporary development outcomes. To trace mechanisms, I leverage a novel panel data set covering the election histories of 931 chiefs in 193 villages. I find evidence of political selection driven by higher barriers to entry for political office: campaigning costs are higher, resulting in both chiefs and the candidate pool as a whole being positively selected. My findings suggest that paying chiefs from a stable source of local revenue can be an efficient tool when top-down monitoring by the State is limited. 

% Abstract
%
%{\bf Crime and Public Housing: A General Equilibrium Analysis}
%
%Abstract
%
%{\bf The Geography of Gang Violence}
%
%Abstract
% 
\end{resume}
\end{document}